\vspace{-2cm} Content of Municipal Government Websites

### 2017-03-29 paper/manuscript.tex
some changes to RD, structural topic models

\noindent We study the content of municipal government websites....

@@

\subsection{Topic modeling}
We hypothesize that a change in leadership from one party to the other will lead to a change in website content because the two parties have different agendas. Democrats have a predilection towards policies that promote social and economic equality, whereas Republicans like to emphasize small government as well as law and order. Documents uploaded to city websites are expected to be a reflection of these preferences. The author-topic model \citep{Rosen-Zvi2004} captures this concept quite well, because it assumes that different authors prefer different topics, each of which is associated with a group of words. We classify all documents that have been present before the change in party control as from one party\footnote{This may be wrong in some cases, as they might be leftovers from yet another predecessor government. If the WaybackMachine data reaches back far enough, we might be able to identify and include only the documents that were added since the previous election.}, and the new documents as stemming from party 2. The number of topics \textit{j} would be set to at least three, where one topic would (hopefully) be reserved for purely administrative, non-partisan issues so that the other two (or more) would resolve to party-specific policy issues. Ideally, the result would then show significant\footnote{Though I am not sure how to calculate that.} differences in the probabilities of authors being assigned to partisan topics.

Alternatively, the more commonplace LDA \cite{Blei2003} is another feasible way of modeling the way in which websites receive a makeover when party control of the mayorship changes. As noted by \citep{Rosen-Zvi2004}, LDA can be considered a special case of the author-topic model, ''where each document has one unique author''. Here, a city website would be a collection of documents, each of which originates entirely from either Democratic or Republican leadership. In a way, this captures the data-generating process more closely.

Even so, neither the author-topic model nor the LDA model are a perfect fit for the structure of city government websites. One assumes that multiple authors write one document. This may be appropriate for the original purpose of author-topic models, scientific papers, which have multiple authors. This is not as good of a fit for city governments however. Using the LDA instead deals with this problem, but it also assumes that one document has multiple topics. For city government websites, this may be an erroneous assumption, because in many cases, each of these files appears to have one very specific purpose - agricultural, parks and recreation, smoke detectors, and so on.

@@

Another problem with these generative models is that they ignore the fact that despite possible changes to websites due to a leadership transition, large parts of the content carry over. This means that unless the successor government decides to delete everything, some of the existing documents will be preserved, and in the model, also attributed to the new 'author'. But the reverse is not possible, because the predecessor government can't choose to retain documents from the future.

One solution might be to rely on LDA models, but only to apply them to documents that were deleted, the strongest possible expression of a successor governments diverging policy preferences. This way, we could identify directly which issues are considered to be the most divisive.

There is also a possibility that city size is a determinant of the number of topics. Larger cities tend to have bigger websites, owing to a larger set of issues that need to be dealt with.

Traditional author models that rely on lexical or syntactic differences may also be of use. Parties and their voters are associated with specific educational backgrounds, which may in turn be associated with specific writing styles. However, it seems likely that personal rather than partisan authorship is playing an even larger role here.

Another option, that I have not looked closely at yet, are (continuous) dynamic topic models by David Blei, which would allow us to model the progression of topics over time, i.e. when party control changes.

>>>>

\noindent We explore the effect of transitions of power in municipal governments on the content of their websites. We hypothesize that when party control changes, city administrators modify the contents of their websites in order to fit the agenda of the new incumbent. To test this theory, we apply an author-topic model [alternatively: structural topic model] to website data acquired from different points in time through the Wayback Machine.

@@

\subsection{Topic modeling}
We hypothesize that a change in leadership from one party to the other will lead to a change in website content because the two parties have different agendas. Democrats have a predilection towards policies that promote social and economic equality, whereas Republicans like to emphasize small government as well as law and order. Documents uploaded to city websites are expected to be a reflection of these preferences.

The Latent Dirichlet Allocation (LDA) \citep{Blei2003} is the most commonly used topic model. However, it is unable to account for the existence of two parties with very different policy agendas, translating to different preferred topics. There are two types of extensions to the LDA that fit our subject much better - the structural topic model, and the author-topic model.

The structural topic model, developed by \cite{Roberts2016a} allows researchers to model a corpus as a function of metadata associated with its documents. Specifically, topic prevalence (the proportion of a document made up by a topic) and topical content (the rate at which words figure into a topic) are contingent on a set of covariates. In our case, the two most important covariates are (1) city and (2) authoring party (operationalized by whether a document was present before a change of power, or introduced afterwards). Furthermore, the population size of the city should be a predictor for both the number and kind of problems it faces, which thus need to be addressed on its website. Furthermore, city size also serves as an estimate for the budget and technical capacities of its staff in charge of maintaining the website\footnote{Although this relationship is not exactly deterministic - when looking through .gov websites manually, I've noticed that a lot of websites of (presumably wealthy)  towns of only a few thousand citizens often have extremely well-kept websites}.  Further demographic as well as economic data might also be useful to differentiate cities from one another. If we model the differences between cities properly, we might not have to/should not include city as a (categorical) variable, because it would probably interfere with these more meaningful covariates.

The author-topic model \citep{Rosen-Zvi2004} would allow us to capture the fact that different authors have different topical preferences. Unfortunately, we have two types of 'authors' - cities, and parties. Given the largely divergent administrative needs of different types of cities, we would likely have to treat cities as the author. This would require us to capture the partisan authorship of different documents entirely on the basis of sub-sets of the website data - changed, added, or deleted documents. (Note: In the papers on author-topic models, the intention is often to analyze scientific articles. These articles are often co-authored. Would it be possible to have BOTH cities and parties as authors, so that a specific version of a website would then be 'co-authored' by its city and party?)

The critical element in this analysis is to accurately attribute authorship of documents to either party. Despite possible changes to websites due to a leadership transition, large parts of the content carry over. This means that unless the successor government decides to delete everything, some of the existing documents will be preserved, and in the model, also attributed to the new 'author'. But the reverse is not possible, because the predecessor government can't choose to retain documents from the future. {\em  This is a very important point for municipal websites. We should investigate the possibility of modeling only the changes---documents that change, documents that are deleted, and documents that are added. }

Labeling newly added documents after a change of power is quite simple. As far as older documents are concerned, we would have to operate under the assumption that the incumbent didn't keep his or her successor's document's on the website for four years.\footnote{Probably a safe assumption. However, we could, and probably should test how long documents tend to stay on a city website. Simple descriptive statistics (for example density plots) on the length of existance should likely be sufficient. If we want to be really fancy about it, we could create a duration model, with document topics as features. This would allow us to measure whether some documents tend to remain longer based on their topic (i.e. fire regulations are probably going to stay up longer than notes on a specific council meeting).} One problem here is the fact that the incumbent would have all the administrative topics assigned to them, simply because they have to have those on their website.

If we really do end up getting swamped with administrative terms in our topic models (and it does kind of look like that at the moment), we might be able to separate the signal from the noise by running a preparatory LDA once and using its results to create a new, corpus-specific list of stop words. After that, we run the actual model. This way, politically charged terms and topics, which likely are not as common, but present nevertheless, should be able to rise to the surface. It might be possible to refine this process by running an exploratory model on website data from cities in which party control never changes, and the incumbent always wins by large margins. 'Safe' cities like this should have fairly homogeneous populations, with little need for the incumbent to play politics on the municipal website. Hence, these websites should be filled with purely administrative content.

The use of asymmetric priors \citep{Wallach2009} in our topic model - i.e. the assumption that some topics, such as administrative content, are inherently more common - may be a more elegant way of dealing with this issue.

Another intervening factor is that for cities in Indiana, mayoral terms begin in January. Since a lot of clerical and administrative tasks tend to be year-specific, work tends to pile up around the new year. Thus it is possible that a spike in newly added documents is not due to a change in party control, but owed to a seasonal increase in activity. We can test for this by comparing election years to non-election years. Furthermore, since in Louisiana, mayors take office in May, we have another point of comparison.

@@

%One solution might be to rely on LDA models, but only to apply them to documents that were deleted, the strongest possible expression of a successor governments diverging policy preferences. This way, we could identify directly which issues are considered to be the most divisive.

%There is also a possibility that city size is a determinant of the number of topics. Larger cities tend to have bigger websites, owing to a larger set of issues that need to be dealt with.

%Traditional author models that rely on lexical or syntactic differences may also be of use. Parties and their voters are associated with specific educational backgrounds, which may in turn be associated with specific writing styles. However, it seems likely that personal rather than partisan authorship is playing an even larger role here.

%another feasible way of modeling the way in which websites receive a makeover when party control of the mayorship changes. As noted by \citep{Rosen-Zvi2004}, LDA can be considered a special case of the author-topic model, ''where each document has one unique author''. Here, a city website would be a collection of documents, each of which originates entirely from either Democratic or Republican leadership. In a way, this captures the data-generating process more closely.

%Even so, neither the author-topic model nor the LDA model are a perfect fit for the structure of city government websites. One assumes that multiple authors write one document. This may be appropriate for the original purpose of author-topic models, scientific papers, which have multiple authors. This is not as good of a fit for city governments however. Using the LDA instead deals with this problem, but it also assumes that one document has multiple topics. For city government websites, this may be an erroneous assumption, because in many cases, each of these files appears to have one very specific purpose - agricultural, parks and recreation, smoke detectors, and so on.+

%\footnote{This may be wrong in some cases, as they might be leftovers from yet another predecessor government. If the WaybackMachine data reaches back far enough, we might be able to identify and include only the documents that were added since the previous election.}, and the new documents as stemming from party 2. The number of topics \textit{j} would be set to at least three, where one topic would (hopefully) be reserved for purely administrative, non-partisan issues so that the other two (or more) would resolve to party-specific policy issues. Ideally, the result would then show significant differences in the probabilities of authors being assigned to partisan topics.

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Sun Mar 26 22:39:59 2017
\begin{table}[ht]
	\centering
	\begin{tabular}{rllllllllllllllll}
		\hline
		Date & Attica & Connersville & Frankfort & Huntingburg & Indianapolis & Lake Station & Linton & Madison & Mitchell & Monticello & North Vernon & Richmond & Rockport & South Bend & Union City & Winchester \\ 
		\hline
		20150701.00 & 20141219004329 & 20090608160638 & 20150801164305 & 20150326174031 & 20080705032706 & 20150801185836 & 20130907112731 & 20150623192440 & 20150801214647 & 20150701005605 & 20150801221031 & 20150702075332 & 20150617220801 & 20150627165751 & 20150925160622 & 20150925022240 \\ 
		20150801.00 & 20160129070621 & 20090608160638 & 20150801164305 & 20151030133234 & 20080705032706 & 20150801185836 & 20130907112731 & 20150801210044 & 20150801214647 & 20150804061315 & 20150801221031 & 20150802055917 & 20150801070026 & 20150726161609 & 20150925160622 & 20150925022240 \\ 
		20150901.00 & 20160129070621 & 20090608160638 & 20150918063903 & 20151030133234 & 20080705032706 & 20150906164302 & 20130907112731 & 20150901105012 & 20150811063416 & 20150905074509 & 20150829185257 & 20150904033112 & 20150909192825 & 20150905085030 & 20150925160622 & 20150925022240 \\ 
		20151001.00 & 20160129070621 & 20090608160638 & 20150925070028 & 20151030133234 & 20080705032706 & 20150908103757 & 20130907112731 & 20150905063305 & 20150811063416 & 20150908082732 & 20150829185257 & 20150921033423 & 20151011085644 & 20151002075030 & 20150925160622 & 20150925022240 \\ 
		20151101.00 & 20160129070621 & 20090608160638 & 20151113140944 & 20151030133234 & 20080705032706 & 20151029043137 & 20130907112731 & 20151110090517 & 20160111041751 & 20151110131337 & 20151103095602 & 20151031212522 & 20151021163057 & 20151101043016 & 20150925160622 & 20151026092123 \\ 
		20151201.00 & 20160129070621 & 20090608160638 & 20151121002259 & 20151030133234 & 20080705032706 & 20151201114611 & 20130907112731 & 20151216063136 & 20160111041751 & 20151115102706 & 20151206224620 & 20151201073504 & 20151212093554 & 20151209044311 & 20160111224058 & 20151127174603 \\ 
		20160101.00 & 20160129070621 & 20090608160638 & 20160110065704 & 20160113165318 & 20080705032706 & 20160101144553 & 20130907112731 & 20151228192543 & 20160111041751 & 20151228224908 & 20160111074656 & 20160102015111 & 20160110195124 & 20151229083812 & 20160111224058 & 20151127174603 \\ 
		20160201.00 & 20160129070621 & 20090608160638 & 20160127035634 & 20160122005059 & 20080705032706 & 20160201195326 & 20130907112731 & 20160201073437 & 20160202113637 & 20160206015204 & 20160111074656 & 20160213102047 & 20160112154213 & 20160206190816 & 20160111224058 & 20160303215247 \\ 
		20160301.00 & 20160330220432 & 20090608160638 & 20160304094239 & 20160221045049 & 20080705032706 & 20160303165533 & 20130907112731 & 20160303181704 & 20160301141845 & 20160304035215 & 20160309122910 & 20160302140643 & 20160112154213 & 20160303175057 & 20160111224058 & 20160303215247 \\ 
		20160401.00 & 20160330220432 & 20090608160638 & 20160321173048 & 20160317192932 & 20080705032706 & 20160404133508 & 20130907112731 & 20160402214824 & 20160405050341 & 20160403012946 & 20160318230947 & 20160403090645 & 20160603041333 & 20160325014215 & 20160111224058 & 20160416084956 \\ 
		20160501.00 & 20160330220432 & 20090608160638 & 20160424080036 & 20160317192932 & 20080705032706 & 20160507020142 & 20130907112731 & 20160504014532 & 20160507154306 & 20160511155648 & 20160420092957 & 20160502154350 & 20160603041333 & 20160427024310 & 20160111224058 & 20160422124026 \\ 
		20160601.00 & 20160330220432 & 20090608160638 & 20160424080036 & 20160317192932 & 20080705032706 & 20160507020142 & 20130907112731 & 20160521233726 & 20160507154306 & 20160522012629 & 20160420092957 & 20160522061744 & 20160603041333 & 20160522075620 & 20160111224058 & 20160517165930 \\ 
		\hline
	\end{tabular}
	\caption{Dates of WaybackMachine snapshots 2015-16} 
\end{table}
